### 2015-02-22 fundamentals/impl.tex
more reduction of excess verbage. Aiming for brevity.

\Cyclus uses a strategy known as \emph{git flow}
\cite{kalliamvakou_code-centric_2014} to manage topical branches where
individuals develop code in parallel and changes are only merged into the
mainline branch after when it is acceptable from a quality control standpoint
All software at this stage must have sufficient successful tests and
comprehensive documentation.  Proposed changes must be sufficiently documented
and tested before they are allowed into \Cyclus.  As an example, a schematic of
the development stages between reporting a bug and merging the fix is shown in
Figure \ref{fig:gitprocess}.

>>>>

\Cyclus uses a strategy known as \emph{git flow}
\cite{kalliamvakou_code-centric_2014} to manage topical branches where
individuals develop code in parallel. All proposed software changes from
topical branches must have sufficient successful tests and comprehensive
documentation to be allowed into \Cyclus.  As an example, a schematic of the
development stages between reporting a bug and merging the fix is shown in
Figure \ref{fig:gitprocess}.
